Malacology: A Programmable Storage System Built on Ceph

### 2016-05-10 paper/paper.tex
Adds 'Policy Durability' section
This is short

-

-

-

>>>>

While storing the code snippets that define the policies in the MDS map is 
possible, it is not recommended as it is an expensive operation (a PAXOS voting 
round). Thus, Malacology only stores policies IDs which correspond to an object 
in a system-maintained pool. When MDSs read a policy, they first check latest 
version from the MDS map, and then dereference the pointer by reading the 
corresponding object in RADOS.
